Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-01-15 ms/manuscript.Rmd
Update MS
- Fix typo in SI units

**`r figure("climate")`** Selected microclimatic variables of study plots along an elevational gradient from \SI{200}{\meter} to \SI{1200}\meter on Moorea, French Polynesia. Relative humidity (RH) and temperature were recorded every \SI{15}{\minute} with dataloggers from `r final_climate_survey$start` to `r final_climate_survey$end`. Vapor pressure deficit (VPD) was calculated from relative humidity and temperature as described in the methods, and overall means calculated for daily mean, minimum, maximum, and standard deviation (SD). 'Epiphytic' dataloggers were placed at \circa{ }\SI{2}{\meter} on trees, and 'terrestrial' dataloggers placed at ground level. Color indicates growth habit: epiphytic dataloggers in green, terrestrial dataloggers in brown. Trendlines fitted using linear models with an interaction between growth habit and elevation (see Methods); all trendlines significant at \pval{ }< 0.05.

>>>>

**`r figure("climate")`** Selected microclimatic variables of study plots along an elevational gradient from \SI{200}{\meter} to \SI{1200}{\meter} on Moorea, French Polynesia. Relative humidity (RH) and temperature were recorded every \SI{15}{\minute} with dataloggers from `r final_climate_survey$start` to `r final_climate_survey$end`. Vapor pressure deficit (VPD) was calculated from relative humidity and temperature as described in the methods, and overall means calculated for daily mean, minimum, maximum, and standard deviation (SD). 'Epiphytic' dataloggers were placed at \circa{ }\SI{2}{\meter} on trees, and 'terrestrial' dataloggers placed at ground level. Color indicates growth habit: epiphytic dataloggers in green, terrestrial dataloggers in brown. Trendlines fitted using linear models with an interaction between growth habit and elevation (see Methods); all trendlines significant at \pval{ }< 0.05.
